QPLIB: A Library of Quadratic Programming Instances

### 2017-01-20 QPLIB.tex
added a few citations, corrected a few typoes
update affiliation

\institute{Fabio Furini \at
           LAMSADE, Universit{\'e} Paris Dauphine, 75775 Paris, France.
           \email{fabio.furini@dauphine.fr}
%
\and
           Emiliano Traversi \at
           LIPN, Universit{\'e} de Paris 13, 93430 Villetaneuse, France.
           \email{emiliano.traversi@lipn.fr}
%
\and       Pietro Belotti \at
           Xpress-Optimizer team, FICO, Birmingham UK
           \email{pietrobelotti@fico.com}
%
\and       Antonio Frangioni \at
           Dipartimento di Informatica, Universit\`a di Pisa,
           Largo B. Pontecorvo 2, 56127 Pisa, Italy,
           \email{frangio@di.unipi.it}
%
\and       Ambros Gleixner \at
           Zuse Institute Berlin, Takustr. 7, 14195 Berlin, Germany.
           \email{gleixner@zib.de}
%
\and       Nick Gould \at
           STFC-Rutherford Appleton Laboratory, Chilton, Oxfordshire OX11 0QX,
           England.
           \email{nick.gould@stfc.ac.uk}
%
\and       Leo Liberti \at
           CNRS LIX, Ecole Polytechnique, 91128 Palaiseau, France.
           \email{liberti@lix.polytechnique.fr}
%
\and       Andrea Lodi \at
           Ecole Polytechnique de Montréal, Canada.               \email{andrea.lodi@polymtl.ca}
%
\and       Ruth Misener \at
           Department of Computing,Imperial College London, UK. \email{r.misener@imperial.ac.uk}
%
\and       Hans Mittelmann \at
           School of Mathematical and Statistical Sciences, Arizona State University,      Tempe, AZ 85287-1804, U.S.A.
\email{mittelmann@asu.edu}
%
\and       Nick Sahinidis \at
Chemical Engineering, Carnegie Mellon University, U.S.A. \email{sahinidis@cmu.edu}
%
\and       Stefan Vigerske \at
           GAMS Software GmbH, P.O. Box 40 59,50216 Frechen, Germany.
           \email{stefan@gams.com}
%
\and       Angelika Wiegele \at
Institut für Mathematik, Alpen-Adria-Universität Klagenfurt, Austria.  \email{angelika.wiegele@aau.at}
           }

>>>>

\institute{Fabio Furini \at
           LAMSADE, Universit{\'e} Paris Dauphine, 75775 Paris, France.
           \email{fabio.furini@dauphine.fr}
%
\and
           Emiliano Traversi \at
           LIPN, Universit{\'e} de Paris 13, 93430 Villetaneuse, France.
           \email{emiliano.traversi@lipn.fr}
%
\and       Pietro Belotti \at
           Xpress-Optimizer team, FICO, Birmingham UK
           \email{pietrobelotti@fico.com}
%
\and       Antonio Frangioni \at
           Dipartimento di Informatica, Universit\`a di Pisa,
           Largo B. Pontecorvo 2, 56127 Pisa, Italy,
           \email{frangio@di.unipi.it}
%
\and       Ambros Gleixner \at
           Zuse Institute Berlin, Takustr. 7, 14195 Berlin, Germany.
           \email{gleixner@zib.de}
%
\and       Nick Gould \at
           STFC-Rutherford Appleton Laboratory, Chilton, Oxfordshire OX11 0QX,
           England.
           \email{nick.gould@stfc.ac.uk}
%
\and       Leo Liberti \at
           CNRS LIX, Ecole Polytechnique, 91128 Palaiseau, France.
           \email{liberti@lix.polytechnique.fr}
%
\and       Andrea Lodi \at
           Ecole Polytechnique de Montréal, Canada.               \email{andrea.lodi@polymtl.ca}
%
\and       Ruth Misener \at
           Department of Computing,Imperial College London, UK. \email{r.misener@imperial.ac.uk}
%
\and       Hans Mittelmann \at
           School of Mathematical and Statistical Sciences, Arizona State University,      Tempe, AZ 85287-1804, U.S.A.
\email{mittelmann@asu.edu}
%
\and       Nick Sahinidis \at
Chemical Engineering, Carnegie Mellon University, U.S.A. \email{sahinidis@cmu.edu}
%
\and       Stefan Vigerske \at
           GAMS Software GmbH, c/o Zuse Institute Berlin, Takustr. 7, 14195 Berlin, Germany.
           \email{svigerske@gams.com}
%
\and       Angelika Wiegele \at
Institut f{\"u}r Mathematik, Alpen-Adria-Universit{\"a}t Klagenfurt, 9020 Klagenfurt am W{\"o}rthersee, Austria.  \email{angelika.wiegele@aau.at}
           }
